%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\cveSubheading}[2]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\pubSubheading}[3]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{1pt}
      \textbf{#1} \\ \vspace{1pt}
      #2 \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\pubSubheadingNewline}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{1pt}
      \textbf{#1} \\ \vspace{1pt}
      \textbf{#2} \\ \vspace{1pt}
      #3 \\
      \textit{\small#4}
    \end{tabular*}\vspace{-7pt}
}



\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\ \vspace{5pt}
      \textit{\small#3} & \textit{\small #4} \\ 
      #5 \\ \vspace{4pt}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={$\bullet$}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Jaewon Hur} \textbf{ /  Post Doctoral Researcher} \\ \vspace{10pt}
    
    School of Cybersecurity and Privacy\\
    Georgia Institute of Technology\\
    United States\\ \vspace{10pt}
    
    \small Phone: (404) 276-8251$|$ Mail: \href{mailto:jwhur19@gmail.com}{\underline{jwhur19@gmail.com}} $|$ 
    Lab: \href{https://gts3.org}{\underline{SSLAB at GT}}
\end{center}

\vspace{15pt}
%------About Me-------
\section{About Me}

Have lots of research experiences across the full stack of computer systems. Have designed a secure data analysis system using confidential computing (i.e., \textbf{DLBox} and \textbf{Secure Spark} presented at \textbf{NDSS 2025)}. Especially familiar with deep learning security (e.g., data extraction attacks). Spearheaded several research projects of confidential computing including efficient confidential serverless (i.e., \textbf{TeeMate}), \emph{syzkaller} extension for SGX libOS (i.e., \textbf{Graminer}), and Intel TDX emulation using \emph{KVM} hypervisor. Initiated and published several RTL fuzzing researches before (i.e., \textbf{DifuzzRTL} at \textbf{S\&P 2021} and \textbf{SpecDoctor} at \textbf{CCS 2022}). Not fully engaged but experienced bug finding in browsers (i.e., \textbf{R2Z2} and \textbf{FuzzOrigin}).

\vspace{10pt}

Interested in system designs in general, and enjoying solving real world problems through programming (e.g., automatic stock trading app \textbf{MumeParrot}).


%-----------EXPERIENCE-----------
\section{Publications}
  \resumeSubHeadingListStart

    \pubSubheading
      {DLBox: New Model Training Framework for Protecting Training Data}
      {\underline{Jaewon Hur}, Juheon Yi, Cheolwoo Myung, Sangyun Kim, Youngki Lee, and Byoungyoung Lee}
      {The 32nd Network and Distributed System Security (NDSS), Feb, 2025.}

    \pubSubheadingNewline
      {Secure Data Analytics in Apache Spark with Fine-grained Policy Enforcement}
      {and Isolated Execution}
      {Byeongwook Kim, \underline{Jaewon Hur}, Adil Ahmad, and Byoungyoung Lee}
      {The 32nd Network and Distributed System Security (NDSS), Feb, 2025.}

    \pubSubheading
      {TeeMate: Fast and Efficient Confidential Container using Shared Enclave}
      {Chulmin Lee, \underline{Jaewon Hur}, Sangho Lee, and Byoungyoung Lee}
      {Arxiv}

    \pubSubheading
      {Graminer: Fuzz Testing Gramine LibOS to Harden the Trusted Computing Base}
      {\underline{Jaewon Hur}, and Byoungyoung Lee}
      {The 6th Workshop on System Software for Trusted Execution (SysTex), May. 2023.}

    \pubSubheading
      {SpecDoctor: Differential Fuzz Testing to Find Transient Execution Vulnerabilities}
      {\underline{Jaewon Hur}, Suhwan Song, Sunwoo Kim, and Byoungyoung Lee}
      {The 29th ACM Conference on Computer and Communication Security (CCS), Nov. 2022.}

    \pubSubheading
      {FuzzOrigin: Detecting UXSS Vulnerabilities in Browsers through Origin Fuzzing}
      {Sunwoo Kim, Youngmin Kim, \underline{Jaewon Hur}, Suhwan Song, and Byoungyoung Lee}
      {The 31st Usenix Security Symposium (SEC), Aug. 2022.}

    \pubSubheading
      {R2Z2: Detecting Rendering Regression in Web Browsers through Differential Fuzz Testing}
      {Suhwan Song, \underline{Jeawon Hur}, Sunwoo Kim, and Byoungyoung Lee}
      {The 44th International Conference on Software Engineering (ICSE), Nov. 2022.}

    \pubSubheading
      {DifuzzRTL: Differential FuzzTesting to Find CPU Bugs}
      {\underline{Jeawon Hur}, Suhwan Song, Dongup Kwon, Eunjin Baek, Jangwoo Kim, and Byoungyoung Lee}
      {The 42nd IEEE Symposium on Security and Privacy (S\&P), May, 2021.}

    \pubSubheading
      {Push Your Password: Secure and Fast WiFi Connection for IoT Devices}
      {Junyoung Choi, \underline{Jaewon Hur}, and Saewoong Bahk}
      {The 17th IEEE Wireless Communication and Networking Conference (WCNC), April, 2021.}

    \pubSubheading
      {EV-CAST: Interference and Energy-Aware Video Multicast Exploiting Collaborative Radio}
      {Yeonchul Shin, \underline{Jaewon Hur}, Gyujin Lee, Jonghoe Koo, Junyoung Choi, Sung-ju Lee, and Sunghyun Choi}
      {The 16th IEEE international Conference on Mobile Ad-Hoc and Smart Systems (MASS), November, 2019.}

  \resumeSubHeadingListEnd

\vspace{10pt}
%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Emulating Intel TDX Machines}}
          {Sep. 2024 -- Now}

        \resumeItemListStart
          \resumeItem
              {Used language: C}
          \resumeItem
              {Used framework: KVM, QEMU}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{ChatGPT based course recommendation bot (Kandl)}}
          {May. 2023 -- Aug. 2023}

        \resumeItemListStart
          \resumeItem
              {Used language: TypeScript, React}
          \resumeItem
              {Used framework: ElasticSearch, Redis, Figma, Next.js}
        \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://github.com/JaewonHur/graminer}{\textbf{\underline{Fuzzing Gramine LibOS}}}}
          {Feb. 2023 -- May. 2023}

        \resumeItemListStart
            \resumeItem
                {Used language: Go, C}
            \resumeItem
                {Used framework: Syzkaller, Gramine LibOS}
            \resumeItem
                {\textbf{Actively used by Intel engineers}}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Automated stock trading app (MumeParrot)}}
          {Sep. 2022 -- Now}

        \resumeItemListStart
            \resumeItem
                {Used language: Kotlin}
            \resumeItem
                {\textbf{Currently available in Android play store}}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Secure policy enforcement in Apache Spark}}
          {May. 2022 -- Dec. 2023}

        \resumeItemListStart
            \resumeItem
                {Used language: Scala}
            \resumeItem
                {Used framework: Spark}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Efficient confidential serverless framework}}
          {May. 2022 -- Dec. 2023}

        \resumeItemListStart
            \resumeItem
                {Used language: C, Scala}
            \resumeItem
                {Used framework: Gramine LibOS, OpenWhisk}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Secure machine learning platform for data protection}}
          {Mar. 2022 -- Apr. 2023}

        \resumeItemListStart
            \resumeItem
                {Used language: Python}
            \resumeItem
                {Used framework: PyTorch, grpc, QEMU-KVM, vfio, AMD-SEV}
            \resumeItem
                {\href{https://github.com/JaewonHur/sev-snp-gpu}{\underline{Running normal Nvidia GPUs in SEV-SNP VMs}}}
        \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://github.com/compsec-snu/specdoctor}{\textbf{\underline{CPU fuzzing to find transient execution vulnerabilities}}}}
          {May. 2021 -- Dec. 2022}

        \resumeItemListStart
            \resumeItem
                {Used language: Scala, Chisel}
            \resumeItem
                {Used framework: RISC-V Boom, RISC-V NutShell, Firesim, Firrtl}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Firmware fuzzing to find bugs in Samsung secure element}}
          {Mar. 2021 -- Feb. 2022}

        \resumeItemListStart
            \resumeItem
                {Used language: C}
            \resumeItem
                {Used framework: QEMU-KVM}
        \resumeItemListEnd


      \resumeProjectHeading
          {\href{https://github.com/compsec-snu/difuzz-rtl}{\textbf{\underline{Differential fuzz testing to find CPU bugs}}}}
          {Sep. 2019 -- May. 2021}

        \resumeItemListStart
            \resumeItem
                {Used language: Scala, Chisel}
            \resumeItem
                {Used framework: RISC-V Boom, RISC-V Rocket, Firrtl}
        \resumeItemListEnd


    \resumeSubHeadingListEnd

\vspace{6pt}
%-----------EDUCATION-----------
\section{Education \& Career}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Georgia Institute of Technology}{Dec. 2024 - \emph{current}}
        {Atlanta GA, United States}{}
        {Post doctorial researcher at sslab (Supervisor: Taesoo Kim)}

    \resumeSubheading
        {Seoul National University}{Sep. 2023 - Nov. 2024}
        {Seoul, South Korea}{}
        {Post doctorial researcher at computer security lab (Supervisor: Byoungyoung Lee)}

    \resumeSubheading
        {Seoul National University}{Mar. 2017 - Aug. 2023}
        {Seoul, South Korea}{}
        {Ph.D. in Electrical and Computer Engineering (Advisor: Byoungyoug Lee)}
        
    \resumeSubheading
      {Pohang University of Science and Technology}{Mar.2013 - Feb. 2017}
      {Pohang, South Korea}{}
      {B.S. in Electronical Engineering}
          
  \resumeSubHeadingListEnd


\vspace{10pt}
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \textbf{Languages}
     \begin{itemize}
      \item \textit{Knowledgeable:} {C, Python, Scala}
      \item \textit{Have an experience with:} {Go, C++, Kotlin, Java, TypeScript} \\
     \end{itemize}
     \textbf{Frameworks}{: AFL, syzkaller, QEMU, kvm, Docker, Kubernetes, Git, Linux, PyTorch, React} \\
    }}
\end{itemize}


%-------------------------------------------
\end{document}
