%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\cveSubheading}[2]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\pubSubheading}[3]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{1pt}
      \textbf{#1} \\ \vspace{1pt}
      #2 \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\pubSubheadingNewline}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{1pt}
      \textbf{#1} \\ \vspace{1pt}
      \textbf{#2} \\ \vspace{1pt}
      #3 \\
      \textit{\small#4}
    \end{tabular*}\vspace{-7pt}
}



\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\ \vspace{5pt}
      \textit{\small#3} & \textit{\small #4} \\ 
      #5 \\ \vspace{4pt}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={$\bullet$}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Jaewon Hur} \textbf{ /  Post Doctoral Researcher} \\ \vspace{10pt}
    
    Dept. of Electrical and Computer Engineering \\
    Seoul National University \\
    South Korea \\ \vspace{10pt}
    
    \small Phone: (+82) 10-2284-1687$|$ Mail: \href{mailto:hurjaewon@snu.ac.kr}{\underline{hurjaewon@snu.ac.kr}} $|$ 
    Lab: \href{https://compsec.snu.ac.kr}{\underline{CompSec at SNU}}
\end{center}

\vspace{15pt}
%------About Me-------
\section{About Me}

I am currently working as a \textbf{post doctoral researcher} at \textbf{Computer Security Lab} of \textbf{Seoul National University}. I received \textbf{Ph.D} at \textbf{Computer Security Lab}, advised by professor \textbf{Byoungyoung Lee} from 2019 to 2023. Before then, I studied at \textbf{multimedia wireless network lab}, advised by professor \textbf{Sunghyun Choi} since 2017 until 2019.

I'm interested in the issues of \textbf{system security} in general, but I focused on two topics during my Ph.D: \textbf{fuzzing}, and \textbf{confidential computing}. As a research, I developed an RTL fuzzer for RISC-V CPUs, named \textbf{DifuzzRTL}, and presented it at \textbf{IEEE S\&P 2021}. In the following research, I developed the first RTL fuzzer that finds transient execution vulnerabilities, named \textbf{SpecDoctor}, presenting it at \textbf{ACM CCS 2022}. After that, I moved to work on \textbf{confidential computing}, especially applying it to solve the issues of data privacy and sovereighty in machine learning. Accordingly, I developed \textbf{FairLearning}, which systematically protects the data from being leaked by untrusted machine learners. In addition, I have guided several research projects about cloud security, such as \textbf{TeeMate} (i.e., efficient confidential serverless computing), and \textbf{Laputa} (i.e., secure policy enforcement in Spark), etc. Currently, I am working on virtualization (i.e., \textbf{KVM}), building secure memory sharing framework for the enclaves.

As above, \textbf{I have studied the topics in system security across the various fields, and I am always willing to learn new security issues}. Besides, I generally like programming and solving the problems on my own, so I developed \textbf{MumeParrot}, which automatically trades stocks for me, and \textbf{Kandl}, which is a ChatGPT based course recommendation bot.

\vspace{10pt}

%-----------EXPERIENCE-----------
\section{Publications}
  \resumeSubHeadingListStart

    \pubSubheadingNewline
      {Laputa: Secure Data Analytics in Apache Spark with Fine-grained Policy Enforcement}
      {and Isolated Execution}
      {Byeongwook Kim, \underline{Jaewon Hur}, Adil Ahmad, and Byoungyoung Lee}
      {under review}

    \pubSubheading
      {TeeMate: Enclave Aliasing for SGX-based Confidential Serverless Computing}
      {Chulmin Lee, \underline{Jaewon Hur}, Sangho Lee, and Byoungyoung Lee}
      {under review}

    \pubSubheading
      {FairLearning: Protecting Training Data from Untrusted Machine Learners}
      {\underline{Jaewon Hur}, Juheon Yi, Cheolwoo Myung, Sangyun Kim, Youngki Lee, and Byoungyoung Lee}
      {under review}

    \pubSubheading
      {Graminer: Fuzz Testing Gramine LibOS to Harden the Trusted Computing Base}
      {\underline{Jaewon Hur}, and Byoungyoung Lee}
      {The 6th Workshop on System Software for Trusted Execution (SysTex), May. 2023.}

    \pubSubheading
      {SpecDoctor: Differential Fuzz Testing to Find Transient Execution Vulnerabilities}
      {\underline{Jaewon Hur}, Suhwan Song, Sunwoo Kim, and Byoungyoung Lee}
      {The 29th ACM Conference on Computer and Communication Security (CCS), Nov. 2022.}

    \pubSubheading
      {FuzzOrigin: Detecting UXSS Vulnerabilities in Browsers through Origin Fuzzing}
      {Sunwoo Kim, Youngmin Kim, \underline{Jaewon Hur}, Suhwan Song, and Byoungyoung Lee}
      {The 31st Usenix Security Symposium (SEC), Aug. 2022.}

    \pubSubheading
      {R2Z2: Detecting Rendering Regression in Web Browsers through Differential Fuzz Testing}
      {Suhwan Song, \underline{Jeawon Hur}, Sunwoo Kim, and Byoungyoung Lee}
      {The 44th International Conference on Software Engineering (ICSE), Nov. 2022.}

    \pubSubheading
      {DifuzzRTL: Differential Fuzz Testing to Find CPU Bugs}
      {\underline{Jeawon Hur}, Suhwan Song, Dongup Kwon, Eunjin Baek, Jangwoo Kim, and Byoungyoung Lee}
      {The 42nd IEEE Symposium on Security and Privacy (S\&P), May, 2021.}

    \pubSubheading
      {Push Your Password: Secure and Fast WiFi Connection for IoT Devices}
      {Junyoung Choi, \underline{Jaewon Hur}, and Saewoong Bahk}
      {The 17th IEEE Wireless Communication and Networking Conference (WCNC), April, 2021.}

    \pubSubheading
      {EV-CAST: Interference and Energy-Aware Video Multicast Exploiting Collaborative Radio}
      {Yeonchul Shin, \underline{Jaewon Hur}, Gyujin Lee, Jonghoe Koo, Junyoung Choi, Sung-ju Lee, and Sunghyun Choi}
      {The 16th IEEE international Conference on Mobile Ad-Hoc and Smart Systems (MASS), November, 2019.}

  \resumeSubHeadingListEnd

\vspace{10pt}
%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Secure and encrypted memory sharing framework for enclaves}}
          {Sep. 2023 -- Now}

        \resumeItemListStart
          \resumeItem
              {Used language: C}
          \resumeItem
              {Used framework: KVM, QEMU, Gramine LibOS}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{ChatGPT based course recommendation bot (Kandl)}}
          {May. 2023 -- Aug. 2023}

        \resumeItemListStart
          \resumeItem
              {Used language: TypeScript, React}
          \resumeItem
              {Used framework: ElasticSearch, Redis, Figma, Next.js}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Fuzzing Gramine LibOS}}
          {Feb. 2023 -- May. 2023}

        \resumeItemListStart
            \resumeItem
                {Used language: Go, C}
            \resumeItem
                {Used framework: Syzkaller, Gramine LibOS}
            \resumeItem
                {\textbf{Actively used by Intel engineers}}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Automated stock trading app (MumeParrot)}}
          {Sep. 2022 -- Now}

        \resumeItemListStart
            \resumeItem
                {Used language: Kotlin}
            \resumeItem
                {\textbf{Currently available in Android play store}}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Secure policy enforcement in data analysis}}
          {May. 2022 -- Dec. 2023}

        \resumeItemListStart
            \resumeItem
                {Used language: Scala}
            \resumeItem
                {Used framework: Spark}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Efficient confidential serverless framework}}
          {May. 2022 -- Dec. 2023}

        \resumeItemListStart
            \resumeItem
                {Used language: C, Scala}
            \resumeItem
                {Used framework: Gramine LibOS, OpenWhisk}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Secure machine learning platform for data protection}}
          {Mar. 2022 -- Apr. 2023}

        \resumeItemListStart
            \resumeItem
                {Used language: Python}
            \resumeItem
                {Used framework: PyTorch, grpc, QEMU-KVM, vfio, AMD-SEV}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{CPU fuzzing for finding transient execution vulnerabilities}}
          {May. 2021 -- Dec. 2022}

        \resumeItemListStart
            \resumeItem
                {Used language: Scala, Chisel}
            \resumeItem
                {Used framework: RISC-V Boom, RISC-V NutShell, Firesim, Firrtl}
        \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Firmware fuzzing to find bugs in Samsung secure element}}
          {Mar. 2021 -- Feb. 2022}

        \resumeItemListStart
            \resumeItem
                {Used language: C}
            \resumeItem
                {Used framework: QEMU-KVM}
        \resumeItemListEnd


      \resumeProjectHeading
          {\textbf{Differential fuzz testing to find CPU bugs}}
          {Sep. 2019 -- May. 2021}

        \resumeItemListStart
            \resumeItem
                {Used language: Scala, Chisel}
            \resumeItem
                {Used framework: RISC-V Boom, RISC-V Rocket, Firrtl}
        \resumeItemListEnd


    \resumeSubHeadingListEnd

\vspace{6pt}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Seoul National University}{Mar. 2017 - Sep. 2023}
        {Seoul, South Korea}{}
        {Ph.D. in Electrical and Computer Engineering (Advisor: Byoungyoug Lee)}
        
    \resumeSubheading
      {Pohang University of Science and Technology}{Mar.2013 - Feb. 2017}
      {Pohang, South Korea}{}
      {B.S. in Electronical Engineering}
          
  \resumeSubHeadingListEnd


\vspace{10pt}
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \textbf{Languages}
     \begin{itemize}
      \item \textit{Knowledgeable:} {C, Python, Scala}
      \item \textit{Have an experience with:} {Go, C++, Kotlin, Java, TypeScript} \\
     \end{itemize}
     \textbf{Frameworks}{: AFL, syzkaller, QEMU, kvm, Docker, Kubernetes, Git, Linux, PyTorch, React} \\
    }}
\end{itemize}


%-------------------------------------------
\end{document}
